Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-07-15 2016-Weak-FH-Bisim/WeakBisim.tex
working on lemma 8 (minor progress)

\begin{lemma}[Weak open transition composition]\label{lem-Weakcompose} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
	Suppose $j_0\in J$ and $\gamma_{j_0}=[\beta_0..\beta_n]$ and additionally:\\[-2ex]
\begin{mathpar}
%\[
P\models{\openrule
	{
		\gamma_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
		\ostate{s_i'^{\, i\in L}}}
}\\
\text{~~and for all $t\in[0..n]$~~}
Q\models{\openrule
	{
		\gamma_{t j}^{j\in J_t},
		 \Pred_t,  
		\Post_t}
	{\ostate{s_{t i}^{i\in L_Q}} \OTWeakarrow {\alpha_t}
		\ostate{s_{(t+1) i}^{\, i\in L_Q}}}
}%\]
\end{mathpar}
Let 
\begin{mathpar}
J_Q=\displaystyle{\bigcup_{t=0}^nJ_{t}}
\qquad
\Pred\,'=\Pred\land \bigwedge_{t=0}^{n}(\alpha_t=\beta_t\land \Pred_t)\bigotimes_{i=t-1}^{0}\Post_i
\\
\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
\Post\,'=\Post\uplus\bigotimes_{t=n}^{0}
		\Post_t
\end{mathpar}
Then, we have\\[-2ex]
	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
			\Pred\,',  \Post\,'
			 }
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
	}
	\]
\end{lemma}
\TODO{Proof starts from here}

\begin{proof} Suppose we have:
\begin{mathpar}
%\[
P\models{\openrule
	{
		\gamma_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
		\ostate{s_i'^{\, i\in L}}}
}
\end{mathpar}
By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
$\forall p\!\in\![0..m_1].P\models\openrule
    {\set{\beta_{1p}},\Pred_{1p},\Post_{1p}   }
         {\ostate{{(s_{1pi})}^{i\in L}} \OTarrow {\tau} \ostate{{(s_{1(p+1)i})}^{i\in L}}} \wedge
P\models\openrule
         {\set{\beta_2},\Pred_2,\Post_2 }
         {\ostate{({s_{20i}})^{i\in L}} \OTarrow {\alpha} \ostate{({s_{21i}})^{i\in L}}}
\wedge\\
\forall p \in [0..m_2].P\models\openrule
         {
           \set{\beta_{3p}},\Pred_{3p}, \Post_{3p}}
         { \ostate{(s_{3pi})^{i\in L}} \OTarrow {\tau} \ostate{(s_{3(p+1)i})^{i\in L}}}$ 
\\
where for all $i\in L$:\\
$s_i=s_{10 i} \wedge s_{1(m_1+1) i}=s_{20i} \wedge  s_{21i}= s_{30 i} \wedge s_{3(m_2+1) i}=s'_i$\\

$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{p=0}^{m_1} \vis{\set{\beta_{1p}}} \dotcup  \vis{\set{\beta_2}} \dotcup \mybigdotcup_{p=0}^{m_2} \vis{\set{\beta_{3p}}}}\\
\Pred=\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\bigotimes_{j=p-1}^{0}\subst{\Post_{1j}}\big)\land\Pred^2\bigotimes_{p=m_1}^{0}\subst{\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\big(\!\!\bigotimes_{j=p-1}^{0}\subst{\Post_{3j}}\subst{\Post_2}\!\! \bigotimes_{p=m_1}^{0}\subst{\Post_{1p}}\big)\\
\Post=\bigotimes_{p=m_2}^{0}\Post_{3p}\subst{\Post_2}\bigotimes_{j=m_1}^{0}\subst{\Post_{1j}}
$\\

Note that, for $l\in\{1,2,3\}$ if $(\beta^l_p)_{j_0}=\tau$ because of Definition \ref{def:Non-ObsTau}, $P$ necessarily makes a $\tau$ open transition and remains in the same state, ($s_p = s_{p+1}$). Thus without loss of generality, we can bypass such an open transition and obtain another decomposition of the WOT without the open transition that requires ${\beta^l_{p{j_0}}}=\tau$. We can thus  suppose that for all $p$ and $l$ we have ${\beta^l_{p{j_0}}}\neq\tau$.

>>>>

\begin{lemma}[Weak open transition composition]\label{lem-Weakcompose} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
	Suppose $j_0\in J$ and $\gamma_{j_0}=[\beta_0..\beta_n]$ and additionally:\\[-2ex]
\begin{mathpar}
%\[
P\models{\openrule
	{
		\gamma_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
		\ostate{s_i'^{\, i\in L}}}
}\\
\text{~~and for all $t\in[0..n]$~~}
Q\models{\openrule
	{
		\gamma_{t j}^{j\in J_t},
		 \Pred_t,  
		\Post_t}
	{\ostate{s_{t i}^{i\in L_Q}} \OTWeakarrow {\alpha_t}
		\ostate{s_{(t+1) i}^{\, i\in L_Q}}}
}%\]
\end{mathpar}
Let 
\begin{mathpar}
J_Q=\displaystyle{\bigcup_{t=0}^nJ_{t}}
\qquad
\Pred\,'=\Pred\land \bigwedge_{t=0}^{n}(\alpha_t=\beta_t\land \Pred_t)\bigotimes_{i=t-1}^{0}\Post_i
\\
\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
\Post\,'=\Post\uplus\bigotimes_{t=n}^{0}
		\Post_t
\end{mathpar}
\TODO{add posts to gammaj's above}
Then, we have\\[-2ex]
	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
			\Pred\,',  \Post\,'
			 }
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
	}
	\]
\end{lemma}

\begin{proof} Suppose we have:
\begin{mathpar}
%\[
P\models{\openrule
	{
		\gamma_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
		\ostate{s_i'^{\, i\in L}}}
}
\end{mathpar}
By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
$\forall p\!\in\![0..m_1].P\models\openrule
    {\set{\beta_{1p}},\Pred_{1p},\Post_{1p}   }
         {\ostate{{(s_{1pi})}^{i\in L}} \OTarrow {\tau} \ostate{{(s_{1(p+1)i})}^{i\in L}}} \wedge
P\models\openrule
         {\set{\beta_2},\Pred_2,\Post_2 }
         {\ostate{({s_{20i}})^{i\in L}} \OTarrow {\alpha'} \ostate{({s_{21i}})^{i\in L}}}
\wedge\\
\forall p \in [0..m_2].P\models\openrule
         {
           \set{\beta_{3p}},\Pred_{3p}, \Post_{3p}}
         { \ostate{(s_{3pi})^{i\in L}} \OTarrow {\tau} \ostate{(s_{3(p+1)i})^{i\in L}}}$ 
\\
where for all $i\in L$:\\
$s_i=s_{10 i} \wedge s_{1(m_1+1) i}=s_{20i} \wedge  s_{21i}= s_{30 i} \wedge s_{3(m_2+1) i}=s'_i$\\
\[\alpha=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}}\]
\[\displaystyle{
\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\Post_{1j}}}}\]
\begin{equation*}
\begin{split}
\Pred&g=\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\bigotimes_{j=p-1}^{0}\subst{\Post_{1j}}\big)\land\Pred^2\bigotimes_{p=m_1}^{0}\subst{\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\big(\!\!\bigotimes_{j=p-1}^{0}\subst{\Post_{3j}}\subst{\Post_2}\!\! \bigotimes_{p=m_1}^{0}\subst{\Post_{1p}}\big)
\\
\Post&=\bigotimes_{p=m_2}^{0}\Post_{3p}\subst{\Post_2}\bigotimes_{j=m_1}^{0}\subst{\Post_{1j}}
\end{split}
\end{equation*}

Note that, for $l\in\{1,2,3\}$ if $\beta^l_{p j_0}=\tau$, then, because of Definition \ref{def:Non-ObsTau}, $P$ necessarily makes a $\tau$ open transition and remains in the same state, ($s_p = s_{p+1}$). Thus without loss of generality, we can bypass such an open transition and obtain another decomposition of the WOT without the open transition that requires ${\beta^l_{p{j_0}}}=\tau$. We can thus  suppose that for all $p$ and $l$ we have ${\beta^l_{p{j_0}}}\neq\tau$.
